---
title: "Final Project Summary Statistics"
subtitle: "Codechella"
authors: "Annie Nadolski, Eleanor McElwee, 
Bryan Hwang, Henry Gresham"
format:
  html:
    df-print: paged
    number-sections: true
    toc: true
    toc-depth: 2
    code-tools: true
    code-overflow: wrap
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
  cache: false
  error: false
---

```{r}
#| label: setup
#| include: false

# Load libraries (install packages in the Console, not in the document)
library(tidyverse)
library(lubridate)

# Reproducibility
set.seed(310)

# Printing / numeric display
options(width = 70)
options(scipen = 99)

# Chunk defaults (optional, but keeps figures consistent)
knitr::opts_chunk$set(
  fig.width  = 5,
  fig.height = 4,
  fig.align  = "center"
  )
```

## Load data

```{r}

bikes<- read.csv("seoul_metro_bike_demand_nokorean.csv", stringsAsFactors = FALSE, check.names = FALSE)
library(dplyr)
train_df <- bikes %>% slice(1:(292 * 24)) # gemini 365x24x.8
test_df <- bikes %>% slice((292 * 24 + 1):n())

print(nrow(train_df)) # Should be 7008
print(nrow(test_df))  # Should be 1752

```

## Summary statistics

```{r}

bikes %>% glimpse()

bikes %>% summary()

ggplot(data = bikes, aes(x = Rented.Bike.Count, y = Temperature..C.)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm")

```

```{r}
# use lubridate package to look at the dates for seasonality (wday(), year(), month(), etc.)
# can use lagged term for a predictor (number of bikes used in each of the previous 12 days in the same hour or number of bikes used at this time last year)

bikes <- bikes %>%
  mutate(
    weekday      = wday(Date, label = TRUE),
    month_name   = month(Date, label = TRUE),
    is_weekend   = factor(ifelse(wday(Date) %in% c(1, 7), 1, 0))
  ) 


ggplot(bikes, aes(x = weekday, y = Rented.Bike.Count)) +
  geom_bar(stat = "identity")

bikes %>% group_by(weekday) %>% 
  summarise(avg_bike_count = mean(Rented.Bike.Count))


```

```{r}


ggplot(bikes, aes(x = month_name, y = Rented.Bike.Count)) +
  geom_bar(stat = "identity")


```
## Feature Engineering Plan
What we are planning to do:
Categorize variables such as humidity, wind speed, and visibility into subgroups such as high humidity, mid humidity, and low humidity

Split up the hours of the day into categories like commuting hours and night time

What we have done (might still need to do more):
Change the date variable into something meaningful, extract weekdays, months, is weekend

Check for high correlation between the variables, for example we have months and seasons, but we only need one. 


## Linear Regression

```{r}
bikes_clean <- bikes %>% 
  select(-Date, -Seasons, -is_weekend) %>% 
  drop_na()

model1 <- lm(Rented.Bike.Count ~ ., data = bikes_clean)

summary(model1)

```
## Road blocks and open questions

Github is currently a roadblock. We need to figure out how to make sure we can all access the data file and know how to collaborate on github. 

There is currently a Korean character in our data file and 3/4 of us have issues reading the file. 

We also want to figure out how to make our bar chart of weekday and count weekday and average count. 

We still need to run our ridge regression.

How do we split the data by time instead of randomly?






